Analyzing the impact of social attributes on commit integration success

### 2017-03-25 Paper/MSRChallenge2017.tex
addressed some other todos

\vspace{1ex}
\noindent\textbf{Metric.} We measure quality software contributions based on the build status of the
commit. We used a decision tree classifier~\cite{Quinlan86} to identify
important factors in predicting build success;  decision tress are well
established  and interpretable. 
We first build a
decision tree classifier using only technical factors, which highlights
the degree to which commit complexity predicts build integration
success.  We then added the social factors to identify the degree to which they
add predictive power to a the initial technical model. 
We use 10-fold cross validation across our evaluation.

@@

It is also worth noting that the Kappa statistic increases in both cases when
adding social data (100\% and 85\% respectively). The Kappa statistic is a more 
robust measure than \textit{correctly classified} instances, since it takes into account the
correctly guessed instances occurring by chance. The mean absolute error also
decreases in both cases, which provides further evidences that social factors
are important when predicting build success.

@@

Based on the decision tree results, we noticed that core team members where
important when classifying build success, so we decided to investigate if core
team members have greater build success rates.
We classified the build success rate for
core team members and non-core team members using the data set without 
downsampling.  We found that core team members
triggered 89.39\% (331827/371208) of the builds in the data set and 75.58\%
(250808/331827) of those builds
passed.  Non-core team members triggered 10.61\% (39381/371208) of the builds 
in the data set
and 64.70\% (25479/39381) of the builds passed.  This shows that core team 
members are more
likely to have a successful build integration than non-core team members.

@@

We also investigated developers with a large number of followers (1000 or more
followers).  We found that 6.94\% (24347/350834) of the contributions in the 
data set were
performed by developers with 1000 or more followers.  We found that these
contributions had a 78.61\% (19138/24347) success rate.  These results show 
developers
with more followers are more likely to have a successful integration build.

>>>>

\vspace{1ex}
\noindent\textbf{Metric.} We measure quality software contributions based on the build status of the
commit. We used a decision tree classifier~\cite{Quinlan86} to identify
important factors in predicting build success;  decision tress are well
established  and interpretable. In particular, we use a J48 decision tree because this classification mechanism has the ability to identify the attributes that discriminate the various instances most clearly, and we are interested in analyzing what particular features can predict with higher accuracy build success.
We first build a
decision tree classifier using only technical factors, which highlights
the degree to which commit complexity predicts build integration
success.  We then added the social factors to identify the degree to which they
add predictive power to a the initial technical model. 
We use 10-fold cross validation across our evaluation.

@@

It is also worth noting that the Kappa statistic increases in both cases when
adding social data (100\% and 85\% respectively). The Kappa statistic is a measurement that also accounts for the accuracy of the predicting power of the model. Furthermore, Kappa is a more 
robust measure than \textit{correctly classified} instances, since it takes into account the
correctly guessed instances occurring by chance. The mean absolute error also
decreases in both cases, which provides further evidences that social factors
are important when predicting build success.

@@

Based on the decision tree results, we noticed that core team members where
important when classifying build success, so we decided to investigate if core
team members have greater build success rates.
We classified the build success rate for
core team members and non-core team members using the data set without 
downsampling.  We found that core team members
triggered 89.39\% (331827/371208) of the builds in the data set and 75.58\%
(250808/331827) of those builds
passed.  Non-core team members triggered 10.61\% (39381/371208) of the builds 
in the data set
and 64.70\% (25479/39381) of the builds passed.  This shows that core team 
members are more
likely to have a successful build integration than non-core team members. We hypothesize the reason for this to be that core team members are more familiar with the code, therefore are more likely to have their builds pass.

@@

We also investigated developers with a large number of followers (1000 or more
followers).  We found that 6.94\% (24347/350834) of the contributions in the 
data set were
performed by developers with 1000 or more followers.  We found that these
contributions had a 78.61\% (19138/24347) success rate.  These results show 
developers
with more followers are more likely to have a successful integration build. Reasons for this might be
